---
title: "graphs"
output: html_document
---

# Imports

```{r}
library(tidyverse)
library(plotly)
library(gganimate)
library(ggcorrplot)
```

# Read in dynasty data

```{r}
dynasty <- readRDS('../../data/dynasty_full.RDS')
dynasty
```
# Read in fantasy data

```{r}
fantasy <- readRDS('../../data/weekly_fantasy.RDS')
fantasy
```


# max_value vs weight by position group

```{r}
dynasty %>% 
  filter(date == max(date)) %>% 
  group_by(name) %>% 
  drop_na(Position) %>%
  ggplot(aes(x = Weight, y = value, color = Position)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_wrap(~Position)
```

# current value vs height by position group

```{r}
dynasty %>% 
  filter(date == max(date)) %>% 
  group_by(name) %>% 
  drop_na(Position) %>%
  ggplot(aes(x = Height, y = value, color = Position)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_wrap(~Position)
```

# current value vs age by position group

```{r}
dynasty %>% 
  filter(date == max(date)) %>% 
  group_by(name) %>% 
  drop_na(Position) %>%
  ggplot(aes(x = Age, y = value, color = Position)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_wrap(~Position)
```

# max_value vs Draft Pick Overall by position group

```{r}
max_val_draft <- dynasty %>% 
  group_by(name) %>% 
  drop_na(Position) %>%
  summarize(max_value = max(value), `Draft Position` = max(`Draft Overall Pick`), position = first(Position)) %>% 
  ggplot(aes(x = `Draft Position`, 
             y = max_value, 
             color = position,
             )) +
    geom_point(aes(text = sprintf("Name: %s<br>Draft Position: %s<br>Max Value: %s<br>Position: %s",
                                name, `Draft Position`, max_value, position
                                ))) +
    geom_smooth(se = FALSE) +
    facet_wrap(~position)

ggplotly(max_val_draft, tooltip = 'text')
```

# Position vs Most Recent Value

```{r}
vals_by_position <- dynasty %>% 
  drop_na(Position) %>% 
  filter(date == max(date)) %>% 
  ggplot(aes(x = Position, y = value, fill = Position)) +
    geom_boxplot()

ggplotly(vals_by_position)
```

# Player comparisons over time, KTC

```{r}
Barkley_Taylor <- dynasty %>% 
  filter(name %in% c("Saquon Barkley", "Jonathan Taylor")) %>% 
  ggplot(aes(x = date, y = value, color = name)) +
    geom_line()

ggplotly(Barkley_Taylor)
```

# Player comparisons over time, fantasy (needs work for readability)

```{r}
BT_2020 <- fantasy %>% 
  filter(full_name %in% c("Saquon Barkley", "Jonathan Taylor"),
         season == 2020) 
  
BT_2021 <- fantasy %>% 
  filter(full_name %in% c("Saquon Barkley", "Jonathan Taylor"),
         season == 2021) 
  
BT_gg <- ggplot(data = fantasy, aes(x = gameday)) +
    geom_line(data = BT_2020, aes(y = fantasy_points_halfppr, color = full_name)) +
    geom_line(data = BT_2021, aes(y = fantasy_points_halfppr, color = full_name))

ggplotly(BT_gg)

```

```{r}
BT_2020 <- fantasy %>% 
  filter(full_name %in% c("Saquon Barkley", "Jonathan Taylor"),
         season == 2020) 
  
BT_2021 <- fantasy %>% 
  filter(full_name %in% c("Saquon Barkley", "Jonathan Taylor"),
         season == 2021) 
  
BT_gg <- ggplot(data = fantasy, aes(x = gameday)) +
    geom_line(data = BT_2020, aes(y = fantasy_points_halfppr, color = full_name)) +
    geom_line(data = BT_2021, aes(y = fantasy_points_halfppr, color = full_name))

#ggplotly(BT_gg)
```


```{r}
BT <- fantasy %>%
  filter(full_name %in% c("Jonathan Taylor", "Saquon Barkley"))

ggplot(BT, aes(x = gameday, fantasy_points_halfppr, color = full_name, label = paste0(round(fantasy_points_halfppr, 0)))) +
         geom_segment(aes(x = gameday, y = 0, yend = fantasy_points_halfppr, xend = gameday), color = "grey50") +
        geom_point(size = 7) +
        geom_text(color = "white", size = 2)
```


# Player compared to mean and max of his position group over time

```{r}
player <- "Antonio Gibson"
pos <- "RB"

player_scores <- fantasy %>% 
  filter(full_name == player)

pos_scores <- fantasy %>% 
  filter(position == pos) %>% 
  group_by(position, week) %>%
  mutate(pos_mean_halfppr = mean(fantasy_points_halfppr),
         pos_max_halfppr = max(fantasy_points_halfppr))

ggplot() +
  geom_line(data = player_scores, aes(x = gameday, y = fantasy_points_halfppr), color = "red")+
  geom_line(data = pos_scores, aes(x = gameday, y = pos_mean_halfppr)) +
  geom_line(data = pos_scores, aes(x = gameday, y = pos_max_halfppr)) +
  transition_reveal(gameday)
```

# Correlation Matrix

```{r, fig.width=10,fig.height=11}
library(GGally)

dynasty %>%
  filter(date == max(date)) %>%
  select(-name, -Drafted, -College, -date, -Born) %>%
  mutate(Experience = as.integer(Experience)) %>%
  ggpairs(title = "Correlations of Dynasty Variables", ggplot2::aes(color = Position), proportions = 20)


```

## Notes from dynasty correlation matrix
  * Age negatively correlates with each position except TE (no correlation). RB strongest.
  * Height only correlates with RB and TE.
  * Weight only correlates with RB value, but it's strong.
  * Draft Class and Experience are perfectly negatively correlated (of course), but Experience, looks like Age but with QBs no longer significant.
  * Draft Round and Draft Overall Pick are obviously nearly perfectly correlated. DOP negatively correlates with each position, though it's weaker for TE (Think Kittle, Waller as influential outliers).
  

```{r}
dyCorr <- dynasty %>%
  filter(date == max(date)) %>%
  select(-name, -Drafted, -College, -date, -Born, -Position) %>%
  cor(use = "pairwise.complete.obs")
  
p.mat <- dynasty %>%
  filter(date == max(date)) %>%
  select(-name, -Drafted, -College, -date, -Born, -Position) %>%
  ggcorrplot::cor_pmat()

p <- ggcorrplot(dyCorr,
           hc.order = TRUE,
           type = "upper",
           p.mat = p.mat,
           colors = c("#E85262", "white", "#136C9D"),
           ggtheme = theme_dark)

ggplotly(p)
```



```{r}
library(corrr)
library(corrplot)

dynasty_college <- dynasty %>%
  filter(date == max(date)) %>%
  select(value, College) %>%
  drop_na(College) %>%
  group_by(College) %>%
  mutate(n = n()) %>%
  filter(n >= 12) %>% 
  arrange(desc(n)) %>%
  select(-n)

dummy <- model.matrix(~0+., data=dynasty_college)

p.mat <- cor_pmat(dummy)

corTrimmed <- cor(dummy, use="pairwise.complete.obs")[,1, drop = FALSE]

cp <- corrplot(corTrimmed,
         type = 'lower',
         cl.pos = 'n',
         method = 'color',
         tl.col = 'black'
         ) 

  # as_tibble() %>% View()
  # ggcorrplot(show.diag = F,
  #            type="upper",
  #            p.mat = p.mat,
  #            insig = "blank"
  #          )
```

## Notes from above

  * Two colleges with at least 12 players in the league shows significant positive correlation
    * LSU
    * Oklahoma
  * Three colleges with at least 12 players in the league show significant negative correlation
    * Oklahoma State
    * South Carolina
    * Notre Dame
  * Positional breakdowns should still be explored; however, those will result in small sample sizes.

```{r}
dynasty_college <- dynasty %>%
  filter(date == max(date)) %>%
  select(value, College) %>%
  drop_na(College) %>%
  group_by(College) %>%
  mutate(n = n()) %>%
  filter(n >= 10) %>% 
  arrange(desc(n)) %>%
  select(-n)

dummy <- model.matrix(~0+., data=dynasty_college)
colnames(dummy) <- sub("College", "", colnames(dummy))

p.matTrimmed <- cor_pmat(dummy)[,1, drop = FALSE]

corTrimmed <- cor(dummy, use="pairwise.complete.obs")[,1, drop = FALSE]

cp <- ggcorrplot(corTrimmed,
           show.diag = F,
           type="lower",
           p.mat = p.matTrimmed,
           insig = "blank"
         )

ggplotly(cp)
```

```{r}
dynasty_college <- dynasty %>%
  filter(date == max(date)) %>%
  select(value, College) %>%
  drop_na(College) %>%
  group_by(College) %>%
  mutate(n = n()) %>%
  filter(n >= 10) %>% 
  arrange(desc(n)) %>%
  select(-n)

dummy <- model.matrix(~0+., data=dynasty_college) 
colnames(dummy) <- sub("College", "", colnames(dummy))

p.matTrimmed <- cor_pmat(dummy)[,1, drop = FALSE]

corTrimmed <- cor(dummy, use="pairwise.complete.obs")[,1, drop = FALSE]

p <- plot_ly(y=rownames(corTrimmed), x=colnames(corTrimmed), 
            z = corTrimmed, 
            type = "heatmap", 
            colorscale= c("red", "white", "blue"),
            showscale = T,
            zmin = -1,
            zmax = 1) %>%
    layout(margin = list(l=120))
p

```

