---
title: "rds_conversions"
output: html_document
---

# Imports

```{r}
library(tidyverse)
library(lubridate)
```

# Read in dynasty values

```{r}
dynasty_historical <- read_csv('../../data/ktc_historical_dynasty_values.csv')
dynasty_historical %>%
  filter(date == max(date))
```

# Read in devy values

```{r}
devy_historical <- read_csv('../../data/ktc_historical_devy_values.csv')
devy_historical %>%
  arrange(date, desc(value))
```

# Read in dynasty attributes

```{r}
dynasty_attributes_long <- read_csv('../../data/ktc_player_attributes.csv')
```

# Widen and prepare dynasty_attributes columns

```{r}
dynasty_attributes_prep <- dynasty_attributes_long %>% 
  pivot_wider(id_cols = name, names_from = attribute, values_from = value) %>%
  mutate(Age = as.integer(str_extract(Age, '\\d+')),
         Born = mdy(Born),
         Height = as.integer(str_extract(Height, '\\d+(?=\')'))*12 + as.integer(str_extract(Height, '\\d+(?=")')),
         Weight = as.integer(str_extract(Weight, '\\d+(?=\\slbs)')),
         `Draft Class` = as.double(`Draft Class`),
         Experience = coalesce(str_extract(`Yrs. Exp.`, "\\d+(?=\\syrs)"), "1"),
         `Draft Round` = as.double(str_extract(Drafted, "\\d(?=,)"))
         )

dynasty_attributes_prep
```

# Bring in pick numbers and positions to create dynasty_attributes

```{r}
draft_picks <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/draft_picks.csv")
# we do a left join here because the names won't always match but don't want to lose any nflscrapR rows
dynasty_attributes <- dynasty_attributes_prep %>%
  left_join(draft_picks %>% 
              filter(position %in% c("QB", "RB", "WR", "TE")) %>% 
              select(pfr_name, season, round, pick, position), 
            by=c("name"="pfr_name", "Draft Class" = "season", "Draft Round" = "round")) %>% 
  select(-`Yrs. Exp.`) %>% 
  rename(Name = name, `Draft Overall Pick` = pick, Position = position)

dynasty_attributes
```

# Read in ktc_historical_dynasty_values as dynasty_values

```{r}
dynasty_values_orig <- read_csv('../../data/ktc_historical_dynasty_values.csv')
```

# Repair duplicate dynasty_values dates

```{r}
# change duplicate entries of 2022-01-05 to 2022-01-06 

dynasty_values <- dynasty_values_orig %>%
  group_by(name, date) %>%
  mutate(Count = row_number()) %>%
  ungroup() %>%
  mutate(date = as.Date(ifelse(Count > 1, date+days(1), date), origin = "1970-01-01")) %>%
  select(-Count) %>%
  arrange(date, desc(value))

dynasty_values
```

# Explote devy_values

```{r}
devy_values_orig <- read_csv('../../data/ktc_historical_devy_values.csv')
```

```{r}
devy_values <- devy_values_orig %>%
  group_by(name, date) %>%
  mutate(Count = row_number()) %>%
  ungroup() %>%
  mutate(date = as.Date(ifelse(Count == 1 & date == "2022-01-11", date-days(1), date), origin = "1970-01-01")) %>%
  select(-Count) %>%
  arrange(date, desc(value))

devy_values
```

# Create master table for shiny app

```{r}
dynasty_full <- dynasty_values %>%
  left_join(dynasty_attributes, by = c('name' = 'Name')) %>% 
  mutate(`Draft Overall Pick` = case_when(name == "D.J. Chark"~61, 
                                          name == "DK Metcalf"~64,
                                          name == "Ronald Jones"~38,
                                          name == "Chris Herndon"~107,
                                          TRUE~`Draft Overall Pick`),
         Position = case_when(name == "D.J. Chark"~"WR",
                              name == "DK Metcalf"~"WR",
                              name == "Robbie Anderson"~"WR",
                              name == "Ronald Jones"~"RB",
                              name == "Chris Herndon"~"TE",
                              TRUE~Position),
         College = ifelse(name == "Melvin Gordon", "Wisconsin", College),
         Experience = as.integer(Experience)
         )

dynasty_full
```


# Rewrite to CSV and RDS

```{r}
# dynasty attributes
dynasty_attributes %>% 
  write_csv('../../data/dynasty_attributes.csv')

dynasty_attributes %>% 
  write_rds('../../data/dynasty_attributes.RDS')

# dynasty values
dynasty_values %>% 
  write_csv('../../data/ktc_historical_dynasty_values.csv')

dynasty_values %>% 
  write_rds('../../data/ktc_historical_dynasty_values.RDS')

# devy values
devy_values %>% 
  write_csv('../../data/ktc_historical_devy_values.csv')

devy_values %>% 
  write_rds('../../data/ktc_historical_devy_values.RDS')

# dynasty values with attributes (aka dynasty_full)
dynasty_full %>%
  write_csv('../../data/dynasty_full.csv')

dynasty_full %>%
  write_rds('../../data/dynasty_full.RDS')

```

